A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-21 paper.tex
2d (8, 8)

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c}
 $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$} & \\ \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$\mr{Map}(\RR^2_{\mathrm{dR}}, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
 \multirow{6}*{$(2,2)$} & \multirow{2}*{\hyperref[sect:2d22minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, T[1](R/\gg))$} & \\  \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d22Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to $R$ matter} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, R/\gg)$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d22Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
 \multirow{2}*{$(\mc N_+, 0)$} & \multirow{2}*{\hyperref[sect:2dN0minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_+ - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$} & \\  \hline
 \multirow{2}*{$(4,0)$} & \multirow{2}*{\hyperref[sect:2d40minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Sect}(\CC, (U \otimes K_\CC^{1/2}) \ham \gg)$} & \\  \hline
 \multirow{2}*{$(2,0)$} & \multirow{2}*{\hyperref[sect:2d20minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
 \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.  When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$. When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.  We can promote the supersymmetry to $\mc N=(8,8)$ when $U = T^*\gg$, but no new twists occur.}
 \label{table_of_twists_2d}
\end{table}

@@

\section{Dimension 2}
The odd part of the $2$-dimensional supersymmetry algebra is 
\[
\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_- .
\]
The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality, where $\Spin(2;\CC)$ acts on $\CC_1, \CC_{-1}$ with weights $1, -1$ respectively.

@@

\subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
The minimal twist is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
By Theorem \ref{3d_4_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$. 
This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang--Mills Theory} \label{sect:2d(8,8)}
Next we consider $\mc N=(8,8)$ supersymmetric Yang--Mills theory.
This theory is the dimensional reduction of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.

The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semi-spin representations.  As in the $\mc N=(4,4)$ case, the classification of square-zero supercharge is identical to the classification we saw in the $\mc N=(4,4)$ case.  Rank $(1,0)$ square zero supercharges, and rank $(1,1)$ square zero supercharges split into two orbits in the following way.

\begin{prop}
There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the $A$- and $B$-supercharges.  The $B$-supercharge occurs as a degeneration of $A$-type supercharges.
\end{prop}

@@

Upon dimensional reduction from 3d $\mc N=8$, the $B$-supercharge reduces to the 2d $\mc N=(8,8)$ $B$-supercharge. 
Indeed, if we forget down to $\mc N=4$ supersymmetry, then the $B$-twist should correspond to the $B$-twist.  In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of $B$-twists lies in the closure of the orbit of $A$-twists.

\subsubsection{Minimal Twist} \label{sect:2d88minimaltwist}
The minimal twist is obtained by the dimensional reduction of the minimal twist of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
Combining Theorem \ref{3d_8_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.

\begin{theorem}
The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$. This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\subsubsection{Topological A Twist} \label{sect:2d88Atwist}
The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
Combining Theorem \ref{thm:3d8Hodgetwist} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.

\begin{theorem}
The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the $A$-twist.  This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.   This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\subsubsection{Topological B Twist} \label{sect:2d88Btwist}
The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
Combining Theorem \ref{cor:3dN8Btwist} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.

\begin{theorem}
The B-twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg / \gg))$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem} \label{thm:2d(N,0)}
The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}

>>>>

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c}
 $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$} & \\ \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$\mr{Map}(\RR^2_{\mathrm{dR}}, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
 \multirow{6}*{$(2,2)$} & \multirow{2}*{\hyperref[sect:2d22minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, T[1](R/\gg))$} & \\  \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d22Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to $R$ matter} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, R/\gg)$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d22Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
 \multirow{2}*{$(\mc N_+, 0)$} & \multirow{2}*{\hyperref[sect:2dN0minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_+ - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$} & \\  \hline
 \multirow{2}*{$(4,0)$} & \multirow{2}*{\hyperref[sect:2d40minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Sect}(\CC, (U \otimes K_\CC^{1/2}) \ham \gg)$} & \\  \hline
 \multirow{2}*{$(2,0)$} & \multirow{2}*{\hyperref[sect:2d20minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
 \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.  When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$. When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.  We can promote the supersymmetry to $\mc N=(8,8)$ when $U = T^*\gg$, but no new twists occur.}
 \label{table_of_twists_2d}
\end{table}

@@

\section{Dimension 2}
The odd part of the $2$-dimensional supersymmetry algebra is 
\[
\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_- .
\]
The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
There is a pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.

@@

\subsubsection{Holomorphic Twist} \label{sect:2d44minimaltwist}
The holomorphic twist is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
By Theorem \ref{3d_4_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$. 
This equivalence is $\mr U(1)$-invariant.
\label{thm:2d44holomorphictwist}
\end{theorem}

@@

\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang--Mills Theory} \label{sect:2d(8,8)}
Next we consider the $\mc N=(8,8)$ supersymmetric Yang--Mills theory.
No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.

The R-symmetry group in the $\mc N=(8,8)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semi-spin representations.  The classification of square-zero supercharges is identical to the classification we saw in the $\mc N=(4,4)$ case.  Rank $(1,0)$ square zero supercharges, and rank $(1,1)$ square zero supercharges split into two orbits in the following way.

\begin{prop}
There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra. The generic orbit consists of A-supercharges and the special orbit consists of B-supercharges.
\end{prop}

@@

The 2d $\cN=(8, 8)$ super Yang--Mills theory may be considered as a 2d $\cN=(4, 4)$ super Yang--Mills theory with matter valued in the symplectic $\fg$-representation $U=T^*\fg$. So, all the computations in this section follow from the corresponding computations in Section \ref{sect:2d(4,4)}.

\subsubsection{Holomorphic Twist} \label{sect:2d88minimaltwist}

From Theorem \ref{thm:2d44holomorphictwist} we obtain the following statement.

\begin{theorem}
The holomorphic twist of the 2d $\mc N=(8,8)$ super Yang--Mills theory is perturbatively equivalent to a holomorphic BF theory with the space of fields given by $T^*[-1]\mr{Map}(\CC, T[1] T^*(\fg/\fg))$. This equivalence is $\mr U(1)$-equivariant.
\end{theorem}

\subsubsection{Topological Twists}
\label{sect:2d88Atwist}
\label{sect:2d88Btwist}

Consider the family of topological supercharges $Q_t$ from Section \ref{sect:2d44Atwist}. From Theorem \ref{thm:2d44Hodgetwist} we obtain the following statement.

\begin{theorem}
The twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the theory $\map(\RR^2_{\mathrm{dR}}, T^*(\fg/\fg)_{\Hod})$. Moreover, the equivalence is $\SO(2, \RR)$-equivariant.
\label{thm:2d88Hodgetwist}
\end{theorem}

\begin{corollary}
The topological A-twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory is perturbatively trivial.
\label{cor:2d88Atwist}
\end{corollary}

\begin{corollary}
The topological B-twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory is perturbatively equivalent to the theory $T^*[-1]\map(\RR^2_{\mathrm{dR}}, T^*(\fg/\fg))$. Moreover, the equivalence is $\SO(2, \RR)$-equivariant.
\label{cor:2d88Btwist}
\end{corollary}

@@

\begin{theorem} \label{thm:2d(N,0)}
The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}
